A 38 Million Year Old Neptune-Sized Planet in the Kepler Field

### 2021-12-06 paper_review/response_1.txt

Dear Dr. Jackson,

We thank you for organizing the review of our paper, and also thank
the referee for constructive criticism.  We have considered the
referee's remarks carefully and revised our manuscript accordingly.

Below, we have reproduced the relevant portions of the referee's
report, alongside our responses. The changes are bolded in the 
attached ms_boldchanges.pdf file, using the trackchanges AASTeX
macros.

@@

RESPONSE
----------
> Done, thank you.

REVIEWER COMMENT
----------
Section 4.1.3 and Figure 6

The significance of this slope is unclear and a sigma is not a good
way to evaluate it. Perform a ratio of chi-squared or F-test to
evaluate it vs. a flat line.

RESPONSE
----------
> The second paragraph of Section 4.1.3 has been modified to mention
> the difference in BIC, and the corresponding approximate Bayes
> factor. 
>
> The slope of $-21 \pm 10\,{\rm min\,day}^{-1}$ is similar to that
> found by \citet{holczer_time_2015}. \added{The $\chi^2$ of the
> best-fit line is $306.1$, with $n=140$ data points.  An alternative
> model of a flat line yields $chi^2=315.6$.  The difference in the
> Bayesian information criterion (BIC) between the two models is ${\rm
> BIC}_{\rm flat} - {\rm BIC}_{\rm line} = 4.5$, which corresponds to a
> Bayes factor of $\approx$9.4. According to the usual
> \citet{kass_bayes_1995} criteria, this is ``positive'' evidence for
> the model with a finite slope.  We view it as suggestive evidence at
> best, particularly given the excess scatter in the transit timing
> measurement uncertainties.}
>
> We have also modified the caption of Figure 6 to clarify that this
> is not a detection.

@@

REVIEWER COMMENT
----------
Line 604-608: The statement that the density from the transit
duration is inconsistent with that expected for the M dwarf "B" cites
Table 2 and Choi+2016, but that Table does not appear to provide any
information on "B", and the Choi+2016 reference is just for the Mesa
models. A density of 2 g/cm3 (or lower) is possible for an M dwarf on
the pre-main sequence, depending on the mass, age and model used.

RESPONSE
----------

(NOTE: TODO: THIS RESPONSE HAS YET TO BE UPDATED WITH A MORE LUCID
DESCRIPTION OF THE DERIVATION OF THE COMPANION MASS)

> Thank you for catching this -- this citation is indeed deprecated
> and erroneously was not updated during the writing process.  The
> final adopted calculation was based on the masses and radii from
> the Baraffe+2015 models, rather than the MESA models (Choi+2016).
> The Baraffe models are available from
> http://perso.ens-lyon.fr/isabelle.baraffe/BHAC15dir/.
>
> We believe that the companion's mass is roughly between 0.3 and 0.4
> Msun, and that the age of the system is ~38 +/- 6 Myr.  The Baraffe
> models give:
>
>    32 Myr 0.300 Msun, 0.481 Rsun, 3.80 g / cm3
>    35 Myr 0.300 Msun, 0.465 Rsun, 4.21 g / cm3
>    40 Myr 0.300 Msun, 0.443 Rsun, 4.86 g / cm3
>    32 Myr 0.400 Msun, 0.555 Rsun, 3.30 g / cm3
>    35 Myr 0.400 Msun, 0.537 Rsun, 3.64 g / cm3
>    40 Myr 0.400 Msun, 0.514 Rsun, 4.15 g / cm3
>    32 Myr 0.330 Msun, 0.506 Rsun, 3.60 g / cm3
>    35 Myr 0.330 Msun, 0.489 Rsun, 3.98 g / cm3
>    40 Myr 0.330 Msun, 0.467 Rsun, 4.58 g / cm3
>
> i.e., our default assumption was 40 Myr and 0.33 Msun.  The age is
> adopted for the reasons discussed in the text.  The mass is based
> off the observed deltaMag in 832nm and K' (3.14 +/- 0.15 and 2.37
> +/- 0.02 respectively), which implies absolute magnitudes for the
> secondary of K'=XXX and [832]=YYY.  Based on a set of absolute
> magnitude and color relations from a submitted paper by A. Kraus,
> these gave ~=0.33 Msun.  (TODO: NEED TO BEEF THIS UP!)
>
> The plausible range of companion densities is therefore 3.30 g/cc
> to 4.86 g/cc.  We've updated the text to reflect this uncertainty,
> but it doesn't change the overall point that our measured stellar
> density (2.00+/-0.24 g/cc) is still a fair bit lower than the
> expected range.

@@

line 670: assuming that SNR is not to blame, the problem is not
precision, the problem is either measuremnt systematics or
astrophysical noise.

RESPONSE
----------
> Thank you for this point; we've updated the text to say
> "signal-to-noise" rather than "precision".

REVIEWER COMMENT
----------
line 678-683: The Ca II HK activity indicator "S" as well as the
H-alpha equivalent width could be obtained from the HIRES spectrum.
Have the authors checked fora X-ray or UV (Galex) detection of this
star? The star is likely not detected but its worth a look. In the
same vein, the authors may wish to comment on whether the star's
infrared emission indicates or rule out a substantial debris disk --
the star is detected in WISE (and perhaps Spitzer?)

RESPONSE
----------

(NOTE: TODO: THIS RESPONSE STILL MIGHT BE UPDATED WITH A POSSIBLE
DEEPER ANALYSIS OF THE UV)

> Regarding the S-values, they are shown in the second panel of
> Figure 7, and are also reported in Table 6.  The line profile
> changes shown in Figure 12 suggested that the majority of the RV
> variation observed was due to starspot-induced variations.
> Quantitative measurements of the H-alpha EWs are not expected to
> change this picture, and so we opt to not include them.
>
> Regarding the NIR, UV, and X-ray detections, we searched Vizier
> within a radius of 4 arcseconds.
>
> For the X-ray (i.e., ROSAT), there were no reported detections in
> Vizier.
>
> For the NIR and the possibility of a debris disk, Kepler-1627 is
> detected in W1, W2, W3, and W4 (see
> kepler1627_vizier_photometry.png attached).  While W4 might be in
> excess of the usual Rayleigh-Jeans tail, and this could be
> quantified by fitting synthetic stellar atmospheres, this type of
> analysis is best done at the population level, particularly given
> the calibration uncertainties that are present in W4 (e.g., Cotten
> & Song 2016, ApJS 225 15).  Since Kepler-1627 has not been
> identified as even a candidate debris disk host in the previous
> literature that performs these population-level infrared excess
> analyses, we opt to not speculate on this topic.
>
> For the UV, Olmedo+2015 reported a coincident source with NUVmag of
> 19.052 +/- 0.017 [AB mags], with a NUV S/N of 65 (2015, ApJ, 813,
> 100). Loyd et al 2020 similarly report a NUV flux of 4e-13 +/-
> 4e-15 mW/m^2, though the latter value is based on the same
> GALEX-CAUSE Kepler survey data presented by Olmedo+2015.  UV
> detections can sometimes be used as a youth indicator (e.g., Figure
> 9 of Newton+2021 AJ 161 65, which Newton et al attribute from the
> idea in Shkolnik+2011, ApJ 727 6).  For Kepler-1627, we have 2MASS
> J = 11.690+/-0.021, and therefore m_NUV-m_J = 7.36.  Given the Gaia
> (BP-RP)0 of 0.977, comparing to Figure 9 of Newton+2021 we find
> that Kepler-1627 overlaps with late-G type stars in Psc-Eri, the
> Pleiades, and the Hyades.  In other words, the UV flux is not a
> particularly strong diagnostic of the age for Kepler-1627 as an
> individual star.  It may well be worth exploring the GALEX-CAUSE
> Kepler survey data for the delta Lyr cluster generally, since the
> later type K and M dwarfs are expected to be elevated with respect
> to the Pleiades and Hyades sequences.  However, this goes beyond
> the scope of the present work, and the combination of the cluster
> membership, stellar rotation, stellar lithium content, and stellar
> activity all point to an age consistent with that reported in our
> work.

### 2021-12-06 paper/ms.tex
update paper and review

\replaced{We then corrected for extinction by querying}{To correct for extinction, we queried} the
3-dimensional maps of \citet{capitanio_threedimensional_2017} and
\citet{lallement_threedimensional_2018}\footnote{\url{https://stilism.obspm.fr/},
2021/09/25}, and applied the extinction coefficients $k_X\equiv
A_X/A_0$ computed by \citet{GaiaCollaboration2018} assuming that $A_0
= 3.1 E(B-V)$.  For \added{UCL, }IC\,2602, the Pleiades, and the \cn, this
procedure yielded a respective mean and standard deviation for the
reddening of \replaced{$E(B-V)=\{0.020\pm0.003, 0.045\pm0.008,
0.032\pm0.006\}$}{$E(B-V)=\{0.084\pm0.041, 0.020\pm0.003, 0.045\pm0.008,
0.032\pm0.006\}$}.
These values \replaced{agree reasonably well with}{are within a
factor of two of} previously reported values
\replaced{from}{in} the literature \replaced{\citep[{\it
e.g.},][]{GaiaCollaboration2018,KounkelCovey2019,bossini_age_2019}}{\citep{pecaut_star_2016,GaiaCollaboration2018,KounkelCovey2019,bossini_age_2019}}\added{,
and are all small enough that the choice of whether to use them {\it vs.} other
extinction estimates does not affect our primary conclusions}.

@@

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Possible evidence for a prograde orbit of Kepler 1627 Ab.} The time of
    each Kepler transit was measured, along with the local slope of
    the light curve.  The two quantities are weakly anti-correlated
    ($\approx$2-$\sigma$), which
    might be caused by starspot crossings during the first
    (second) half of transit inducing a positive (negative) TTV,
    provided that the orbit is prograde \citep{mazeh_time_2015}.  The
    units along the abscissa can be understood by considering that the
    stellar flux changes by $\sim$60\,ppt per half rotation period
    ($\sim$1.3\,days).
		\label{fig:corr}
	}
\end{figure}

@@

We therefore isolated each of the 144 observed transits to within
$\pm4.5$\,hr of each transit, and fitted each window with both {\it
i)} a local \added{second or fourth-order }polynomial baseline plus the transit, and {\it ii)} a local linear
trend\added{ plus the transit}.  \deleted{We considered the results both for a second and fourth-order
time-dependence in the local baseline.  }We let the mid-time of each
transit float, and then calculated the residual between the measured
mid-time and that of a periodic orbit.  This residual, the transit
timing variation, is plotted in Figure~\ref{fig:corr} against
the local linear slope for the fourth-order polynomial baseline.  The
slope of $-21 \pm 10\,{\rm min\,day}^{-1}$ is similar to that
found by \citet{holczer_time_2015}.

One concern we had in this analysis was whether our transit fitting
procedure might induce spurious correlations between the slope and
transit time.  In particular, using the second-order polynomial
baseline yielded a larger anti-correlation between the TTVs and local
slopes, of $-79 \pm 14\,{\rm min\,day}^{-1}$.  We therefore
performed an injection-recovery procedure in which we injected
transits at different phases in the \sn\ light curve and repeated the
TTV analysis.  This was done at $\approx$50 phases, each separated by
$0.02\,P_{\rm orb}$ while omitting the phases in transit.  For
the second-order polynomial baseline, this procedure yielded
a similar anti-correlation in the injected transits as that present in the real
transit;
using this baseline would therefore bias the
result.  However for the fourth-order baseline, the correlation
present in the data was stronger than in all but one of the injected
transits.
Possible interpretations are discussed below. Given the
\added{lack of }statistical significance, this analysis should be interpreted as
suggestive at best.

@@

\added{We used the ephemeris of \citet{holczer_transit_2016} to
observe a transit of \pn\ on the night of 2021 Aug 7 both
spectroscopically and photometrically.  We used the HIRES echelle
spectrograph at the Keck-I telescope and MuSCAT3 at Haleakal\=a
Observatory on Maui, HI \citep{Narita_2020}.} \deleted{ We monitored
\sn\ with Keck/HIRES before, during, and after transit on the night of
2021 Aug 7.} \replaced{We used the iodine cell for wavelength
calibration}{For the HIRES wavelength calibration, we used the iodine
cell}, and extracted the 1-D spectra using the standard California
Planet Survey pipeline \citep{howard_cps_2010}.  \added{Given the
faintness of the target ($V=13.1$), we observed using the C2 decker,
which yielded an instrument resolution of $\approx$50{,}000.} The
airmass ranged between 1.1 and 2.2 from the start through the end of
observations; the seeing ranged from $1\farcs1$ at the beginning to
$1\farcs5$ at the end.  \added{The HIRES exposure time was set at
$\approx$15 minutes in order to resolve the 2.8 hour transit event,
which yielded a S/N per resolution element of $\approx 75$ (low for
precision radial velocity standards).} \replaced{We also
simultaneously observed across {\it griz} bands using MuSCAT3 at
Haleakal\=a Observatory on Maui, HI.}{For the MuSCAT3 observations, we
observed simultaneously across the {\it griz} bands.} \added{The
exposure times in each bandpass ranged between 23 and 46 seconds, and
were chosen in order to yield a S/N in the peak pixel that exceeded
130 while also preventing saturation.} Performing aperture photometry
on the latter image stack yielded the data given in
Table~\ref{tab:phot}.

@@

\listofchanges

>>>>

\replaced{We then corrected for extinction by querying}{To correct for extinction, we queried} the
3-dimensional maps of \citet{capitanio_threedimensional_2017} and
\citet{lallement_threedimensional_2018}\footnote{\url{https://stilism.obspm.fr/},
2021/09/25}, and applied the extinction coefficients $k_X\equiv
A_X/A_0$ computed by \citet{GaiaCollaboration2018} assuming that $A_0
= 3.1 E(B-V)$.  For \added{UCL, }IC\,2602, the Pleiades, and the \cn, this
procedure yielded a respective mean and standard deviation for the
reddening of \replaced{$E(B-V)=\{0.020\pm0.003, 0.045\pm0.008,
0.032\pm0.006\}$}{$E(B-V)=\{0.084\pm0.041, 0.020\pm0.003, 0.045\pm0.008,
0.032\pm0.006\}$}.
These values \replaced{agree reasonably well with}{are within a
factor of two of} previously reported values
\replaced{from}{in} the literature \citep{pecaut_star_2016,GaiaCollaboration2018,KounkelCovey2019,bossini_age_2019}\added{, and are all small enough that the choice of whether to use them {\it vs.} other
extinction estimates does not affect our primary conclusions}.

@@

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf \replaced{Possible}{Weak} evidence for a prograde orbit of Kepler 1627 Ab.} The time of
    each Kepler transit was measured, along with the local slope of
    the light curve.  The two quantities \replaced{are weakly}{might
    be} anti-correlated
    ($\approx$2-$\sigma$), which
    \replaced{might}{could} be caused by starspot crossings during the first
    (second) half of transit inducing a positive (negative) TTV,
    provided that the orbit is prograde \citep{mazeh_time_2015}.  The
    units along the abscissa can be understood by considering that the
    stellar flux changes by $\sim$60\,ppt per half rotation period
    ($\sim$1.3\,days).
		\label{fig:corr}
	}
\end{figure}

@@

We therefore isolated each of the 144 observed transits to within
$\pm4.5$\,hr of each transit, and fitted each window with both {\it
i)} a local \added{second or fourth-order }polynomial baseline plus the transit, and {\it ii)} a local linear
trend\added{ plus the transit}.  \deleted{We considered the results both for a second and fourth-order
time-dependence in the local baseline.  }We let the mid-time of each
transit float, and then calculated the residual between the measured
mid-time and that of a periodic orbit.  This residual, the transit
timing variation, is plotted in Figure~\ref{fig:corr} against
the local linear slope for the fourth-order polynomial baseline.  The
slope of $-21 \pm 10\,{\rm min\,day}^{-1}$ is similar to that
found by \citet{holczer_time_2015}. \added{The $\chi^2$ of the
best-fit line is $306.1$, with $n=140$ data points.  An alternative
model of a flat line yields $\chi^2=315.6$.  The difference in the
Bayesian information criterion (BIC) between the two models is ${\rm
BIC}_{\rm flat} - {\rm BIC}_{\rm line} = 4.5$,
which corresponds to a Bayes factor of $\approx$9.4. According to the
usual \citet{kass_bayes_1995} criteria, this is ``positive'' evidence
for the model with a finite slope.  We view it as suggestive evidence
at best, particularly given the excess scatter in the transit timing
measurement uncertainties.}

\replaced{One}{A separate} concern we had in this analysis was whether our transit fitting
procedure might induce spurious correlations between the slope and
transit time.  In particular, using the second-order polynomial
baseline yielded a larger anti-correlation between the TTVs and local
slopes, of $-79 \pm 14\,{\rm min\,day}^{-1}$.  We therefore
performed an injection-recovery procedure in which we injected
transits at different phases in the \sn\ light curve and repeated the
TTV analysis.  This was done at $\approx$50 phases, each separated by
$0.02\,P_{\rm orb}$ while omitting the phases in transit.  For
the second-order polynomial baseline, this procedure yielded
a similar anti-correlation in the injected transits as that present in the real
transit;
using this baseline would therefore bias the
result.  However for the fourth-order baseline, the correlation
present in the data was stronger than in all but one of the injected
transits.
Possible interpretations are discussed below. Given the
\added{lack of }statistical significance, this analysis should be interpreted as
suggestive at best.

@@

\added{We used the ephemeris of \citet{holczer_transit_2016} to
observe a transit of \pn\ on the night of 2021 Aug 7 both
spectroscopically and photometrically.  We used the HIRES echelle
spectrograph at the Keck-I telescope and the MuSCAT3 photometer at Haleakal\=a
Observatory on Maui, HI \citep{Narita_2020}.} \deleted{ We monitored
\sn\ with Keck/HIRES before, during, and after transit on the night of
2021 Aug 7.} \replaced{We used the iodine cell for wavelength
calibration}{For the HIRES wavelength calibration, we used the iodine
cell}, and extracted the 1-D spectra using the standard California
Planet Survey pipeline \citep{howard_cps_2010}.  \added{Given the
faintness of the target ($V=13.1$), we observed using the C2 decker,
which yielded an instrument resolution of $\approx$50{,}000.} The
airmass ranged between 1.1 and 2.2 from the start through the end of
observations; the seeing ranged from $1\farcs1$ at the beginning to
$1\farcs5$ at the end.  \added{The HIRES exposure time was set at
$\approx$15 minutes in order to resolve the 2.8 hour transit event,
which yielded a S/N per resolution element of $\approx 75$ (low for
precision radial velocity standards).} \replaced{We also
simultaneously observed across {\it griz} bands using MuSCAT3 at
Haleakal\=a Observatory on Maui, HI.}{For the MuSCAT3 observations, we
observed simultaneously across the {\it griz} bands.} \added{The
exposure times in each bandpass ranged between 23 and 46 seconds, and
were chosen in order to yield a S/N in the peak pixel that exceeded
130 while also preventing saturation.} Performing aperture photometry
on the latter image stack yielded the data given in
Table~\ref{tab:phot}.

@@

%\listofchanges
